---
title: "Summary Plots for Factorial Designs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Summary Plots for Factorial Designs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ARCmisc)
library(ggplot2)
```


The `gg_sum` function can be used to create simple summaries of data from factorial experiments.
Like all functions in this packages, they are created to simplify code that I commonly have to write.


# Data

To start, let us use the `mtcars` dataset to make some simple plots.
Just as a note, this plotting function is meant to plot 1 continuous variable,
on the y-axis and then use factors to plot on the x-axis, color, or facets.

```{r}
mt2 = mtcars
mt2$cyl = as.factor(mtcars$cyl)
mt2$am = as.factor(mtcars$am)
```

# Simple one-way plot

## Default

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = cyl
) + theme_classic()
```

## Customized

The plots have customizing features.

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = cyl,
  sum_color = "skyblue",
  point_color = "skyblue",
  point_alpha = .5,
) + theme_classic()
```

# Adding groups

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = cyl,
  group = am,
) + theme_classic()
```

## Customized

The dots need to have the fill aspect also applied.

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = cyl,
  group = am,
  point_alpha = .5,
  sum_alpha = .6
) + 
  scale_color_viridis_d(end = .8) +
  scale_fill_viridis_d(end = .8) +
  theme_classic()
```

# Facets

Rather than, or in addition to, facets can be applied.

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = am,
  panel = cyl,
  trace = FALSE,
  point_alpha = .5,
) + theme_classic()
```

# Bigger Data

The plots above really only work with small datasets. I have other features for
larger datasets.

```{r}
data("ChickWeight")
cw = ChickWeight
cw$time = as.factor(cw$Time)
cw$diet = as.factor(cw$Diet)
cw = cw[which(as.numeric(cw$Time) < 8),]
```

## No Grouping

We can suppress the points and plot a "slab" instead

```{r}
gg_sum(cw,
       x = time,
       y = weight,
       sum_color = "darkgrey",
       sum_alpha = .5,
       show_points = FALSE,
       show_slab = TRUE,
       err_width = .2) 
```

## Groups

```{r}
gg_sum(cw,
       x = time,
       y = weight,
      group = diet,
       show_points = FALSE,
       #show_slab = TRUE,
       err_width = .2) + 
  scale_color_viridis_d(end = .8) +
  scale_fill_viridis_d(end = .8) +
  theme_classic()
```
