---
title: "Simple Summary Plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple Summary Plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
references: references.json
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ARCmisc)
library(ggplot2)
```


The `gg_sum` function can be used to create simple summaries of data from factorial experiments. 
The `gg_ident` function is meant to be used to visualize paired comparisons.
Like all functions in this packages, they are created to simplify code that I commonly have to write.


# Data

To start, let us use the `mtcars` dataset to make some simple plots.
Just as a note, this plotting function is meant to plot 1 continuous variable,
on the y-axis and then use factors to plot on the x-axis, color, and/or facets.

```{r}
mt2 = mtcars
mt2$cyl = as.factor(mtcars$cyl)
mt2$am = as.factor(mtcars$am)
```

For the `gg_ident` example, we will use the `iris` data.

# Simple one-way plot

## Default

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = cyl
) + theme_classic()
```

## Customized

The plots have customizing features.

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = cyl,
  sum_color = "skyblue",
  point_color = "skyblue",
  point_alpha = .5,
) + theme_classic()
```

# Adding groups

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = cyl,
  group = am,
) + theme_classic()
```

## Customized

The dots need to have the fill aspect also applied.

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = cyl,
  group = am,
  point_alpha = .5,
  sum_alpha = .6
) + 
  scale_color_viridis_d(end = .8) +
  scale_fill_viridis_d(end = .8) +
  theme_classic()
```

# Facets

Rather than, or in addition to, facets can be applied.

```{r}
gg_sum(
  data = mt2,
  y = mpg,
  x = am,
  panel = cyl,
  trace = FALSE,
  point_alpha = .5,
) + theme_classic()
```

# Bigger Data

The plots above really only work with small datasets. I have other features for
larger datasets.

```{r}
data("ChickWeight")
cw = ChickWeight
cw$time = as.factor(cw$Time)
cw$diet = as.factor(cw$Diet)
cw = cw[which(as.numeric(cw$Time) < 8),]
```

## No Grouping

We can suppress the points and plot a "slab" instead

```{r}
gg_sum(cw,
       x = time,
       y = weight,
       sum_color = "darkgrey",
       sum_alpha = .5,
       show_points = FALSE,
       show_slab = TRUE,
       err_width = .2) 
```

## Groups

```{r}
gg_sum(cw,
       x = time,
       y = weight,
      group = diet,
       show_points = FALSE,
       #show_slab = TRUE,
       err_width = .2) + 
  scale_color_viridis_d(end = .8) +
  scale_fill_viridis_d(end = .8) +
  theme_classic()
```

# Line-of-Identity Plots

In some cases, we may have simple paired comparisons. Imagine that the `iris` data contains 4 measures under 4 separate conditions. 
You may want to compare the differences between the conditions. 
Therefore, you can use a line-of-identity (sometimes called "line of equality") 
plot to determine the differentiation between the conditions. 
This plot is good to use in these scenarios because the line can be viewed as
the demarcation point a positive or negative effect.
The more data points shifted in one direction would then indicate a stronger
size/direction of effect.

```{r}
gg_ident(x = Sepal.Width,
         y = Sepal.Length,
         data = iris)
```

## Indicate Groupings

The `group` or `panel` arguments can also be utilized.

```{r}
gg_ident(x = Sepal.Width,
         y = Sepal.Length,
         data = iris,
         group = Species)
```
```{r}
gg_ident(x = Sepal.Width,
         y = Sepal.Length,
         data = iris,
         panel = Species)
```
# Waterfall Plots

In pre-post style studies, it may be useful to display the data using waterfall plot.
These plots can show the distribution of responses relative to no effect (zero).

```{r}
set.seed(5467)
df = data.frame(y = rnorm(30),
                group = c(rep("A",15),rep("B",15)))

gg_wf(y=y,
      group = group,
      panel = group,
      data = df) +
  theme_bw()

```

