---
title: "Wilcoxon-Mann-Whitney Odds"
subtitle: "A Rank Based Hypothesis Test"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Wilcoxon-Mann-Whitney Odds}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ARCmisc)
```

# Short Background

As an alternative, or in supplement to, Wilcoxon-Mann-Whitney rank sum/signed rank tests @agresti1980 and @wmw_odds have suggested a measure of effect size in the form of "odds" [@wmw_odds; @agresti1980]. This can be considered as a transformation of the rank-biserial correlation or the concordance probability[^1]

[^1]: You can see this in blog posts by [Frank Harrell](https://www.fharrell.com/post/wpo/) or in the [effectsize R package](https://easystats.github.io/effectsize/)

# Implementation

This is implemented with the `wmw_odds` function. It is almost identical to `wilcox.test`

## Two sample

```{r}
data(sleep)

wmw_otest(extra ~ group,
         data = sleep)
```

## Paired samples

```{r}
data(sleep)

wmw_otest(extra ~ group,
         data = sleep,
         paired = TRUE)
```

## One sample

```{r}
data(sleep)

wmw_otest(sleep$extra)
```

# References
